Abstractions for Multi-Sorted Substitutions

### 2023-08-01 paper/paper.tex
Update.

  \ExampleCode\FExampleSub

@@

  \subsection{Unifying Renamings \& Substitutions}
  A well-known problem with DeBruijn-indices is that the operation of
  applying a substitution \texttt{σ} to a term \texttt{t} cannot be
  defined directly by structural recursion on \texttt{t}.
  If \texttt{t} is a term like \texttt{λx e},
  where the subterm \texttt{e} is under a binder, we need to adjust \texttt{σ}
  for the shifted DeBruijn-indices in \texttt{e}:
  \begin{itemize}
  \item The variable \texttt{zero} refers in \texttt{e} to the variable bound by the binder.
  \item a variable \texttt{suc x} refers to variable \texttt{x} in \texttt{σ}.
  \end{itemize}

>>>>

  For example, the substitution, which replaces the term variable 0 with the
  identity function and the type variable 1 with the bottom type, is defined
  as followed:
  \ExampleCode\FExampleSub

@@

  \subsection{Unifying Renamings \& Substitutions}
  A well-known problem with DeBruijn-indices is that the operation of
  applying a substitution \texttt{σ} to a term \texttt{t} cannot be
  defined directly by structural recursion on \texttt{t}.
  If \texttt{t} is a term like \texttt{λx e},
  where the subterm \texttt{e} is under a binder, then the variables
  in \texttt{e} are shifted, i.e.  the variable \texttt{zero} refers
  to the variable from the binder, whereas a variable \texttt{suc x}
  refers to the variable \texttt{x} from outside of the binder.
  As the terms contained in \texttt{σ} may themselves contain free variables,
  they need to be shifted, too, before they can be substituted
  for variables in \texttt{e}. 
  Shifting the variables in a term is itself a substitution, which maps
  each variable \texttt{x} to the term \texttt{` (suc x)}.
  However, applying this shifting substitution to the terms in
  \texttt{σ} is not structurally recursive, as the terms in \texttt{σ}
  are not subterms of \texttt{λx e}.
